Automated Formal Synthesis\\ of Safe Digital Controllers for Continuous Plants

### 2019-01-23 automatica/paper.tex
decided I didn't like experimental goal 2
seems silly because Matlab isn’t sound

Using the state-space models described in Section~\ref{exp:benchmarks}, 
the evaluation study has the following two experimental goals:

@@

\item[EG2] \textbf{(Sanity check)} Confirm the stability \note{also?} and safety of the synthesized controllers outside 
of our model representation using MATLAB. 
%\note{Where is this done?}

@@

\textcolor{blue}{The synthesized controllers are confirmed to be safe outside of our model
representation using MATLAB, achieving EG2 \note{please explain how this check is performed - is the check itself sound?}.  
A~link to the full experimental environment, including scripts to reproduce the results, all
benchmarks and the tool, is provided in the
footnote as an Open Virtual Appliance (OVA).\footnote{\url{XXXX}}
The provided experimental environment runs multiple discretisations for each
benchmark, and lists the fastest as the result synthesis time.}

>>>>

Using the state-space models described in Section~\ref{exp:benchmarks}, 
the evaluation study has the following experimental goal:

@@

%\item[EG2] \textbf{(Sanity check)} Confirm the stability \note{also?} and safety of the synthesized controllers outside 
%of our model representation using MATLAB. 
%\note{Where is this done?}

@@

%\textcolor{blue}{The synthesized controllers are confirmed to be safe outside of our model
%representation using MATLAB, achieving EG2 \note{please explain how this check is performed - is the check itself sound?}.  
A~link to the full experimental environment, including scripts to reproduce the results, all
benchmarks and the tool, is provided in the
footnote as an Open Virtual Appliance (OVA).\footnote{\url{XXXX}}
The provided experimental environment runs multiple discretisations for each
benchmark, and lists the fastest as the result synthesis time.
